---
title: "SCORE - Tremoliere Generalizability of Claim 4"
author: "Zachariah Berry"
date: "12/17/2021"
output: 
  html_document:
    theme: flatly
    code_folding: hide
    toc: true
    toc_depth: 4
    toc_float: true
    number_sections: true
---

# Libraries

Below are the libraries that need to be loaded in order to run the code in this RMarkdown file.

```{r, include =F}
library(tidyverse)
library(stats)
library(emmeans)
library(kableExtra)
library(Rmisc)
library(car)
library(reshape2)
library(lme4)
library(lmerTest)
library(sjPlot)
library(pwr)
library(rstatix)
```

# Read in data and clean

```{r}
df <- read.csv("Tremoliere_generalizability_score.csv")
# check how many people provided an "appropriate" response to the manipulation
with(df, table(satisfactory_manipulation_response1))
# re-structure data so that it's in long form 
df2 <- melt(df[,c("moral_accept", "moral_accept1","ResponseId",
                  "death_salience","pain_salience","satisfactory_manipulation_response1",
                        "age","gender", "gender_3_TEXT", "politic_1","politic_2","politic_3", "race",
                        "race_7_TEXT","race_8_TEXT","income","education","open","cond","salience", "participant_uid")],
              id.vars = c("ResponseId","death_salience","pain_salience","satisfactory_manipulation_response1",
                        "age","gender", "gender_3_TEXT", "politic_1","politic_2","politic_3", "race",
                        "race_7_TEXT","race_8_TEXT","income","education","open","cond","salience", "participant_uid"),
              value.name = "moral_acceptability")#
# remove responses that did not proprely respond to the manipulation
df2 <- df2 %>% 
  filter(satisfactory_manipulation_response1 == 1)
# create moral acceptability measure where morally acceptable is 1 and 
df2 <- df2 %>% 
  mutate(moral_acceptability_01 = case_when(
         moral_acceptability == "1" ~ 0,
         moral_acceptability == "2" ~ 1))
# create a variable for the different moral dilemma outcomes
df2 <- df2 %>% 
  mutate(moral_scenario = case_when(
    variable == "moral_accept" ~ "impartial_beneficience",
    variable == "moral_accept1" ~ "partial_beneficience"
  ))
# set variables to their type
df2 <- df2 %>% 
  mutate(salience_fact = as.factor(salience),
         moral_scenario_fact = as.factor(moral_scenario))
```

# Descriptive Visualization

## Moral acceptability by salience condition (death, pain) and outcome (impartial, partial)

```{r}
df2 %>% 
  ggplot() + 
  aes(x = moral_acceptability_01, group = salience) + 
  geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat = "count") + 
  scale_y_continuous(labels = scales::percent) + 
  scale_x_continuous(breaks = c(0,1), labels = c("not moral","moral")) +
  facet_grid(.~salience*moral_scenario)
```

# Analysis

```{r}
# fit logistic regression model with random intercept for participant id
fit10 <- glmer(moral_acceptability_01 ~ salience*moral_scenario + (1|participant_uid),data = df2, 
               family=binomial, control = glmerControl(optimizer = "bobyqa"))
# summarize results of model
summary(fit10)
# get table with odds ratios
tab_model(fit10)
```


# Original Paper Analysis

Below, I analyze the results with an ANOVA in line with how the original paper conducted the analysis. This analysis will not be used to assess a successful generalizability of the original claim. 

```{r}
fit4 <- anova_test(data = df2, dv = moral_acceptability_01, wid = participant_uid,
                   between = salience_fact, within = moral_scenario_fact)
get_anova_table(fit4)
```

